On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages

### 2020-10-10 paper/paper.tex
Some changes suggested by Mark

A major benefit of the Haskell language is that it is frequently possible derive
a Haskell implementation from a specification, either partially or fully.  This
technique is used extensively, for example, in \cite{Bird:2010:Pearls} and
\cite{Gibbons:2002:Calc}.  Recent examples of this technique include the work in
\cite{Elliott-2018-ad-icfp} as well as the work in
\cite{Elliott2019-convolution-extended}.  When it is not possible to fully
derive an implementation from a specification, it is often easier to check a
Haskell implementation against a specification than it is in many imperative
languages due, in part, to the management of side effects in Haskell. This is
more difficult to do using an imperative language such as C, as they provide no
restrictions on where side effects can occur.

@@

Note that the instance definition is automatically generated from the
\ttt{Generic} instance.

>>>>

A major benefit of the Haskell language is that it is frequently possible to derive
a Haskell implementation from a specification, either partially or fully.  This
technique is used extensively, for example, in \cite{Bird:2010:Pearls} and
\cite{Gibbons:2002:Calc}.  Recent examples of this technique include the work in
\cite{Elliott-2018-ad-icfp} as well as the work in
\cite{Elliott2019-convolution-extended}.  When it is not possible to fully
derive an implementation from a specification, it is often easier to check a
Haskell implementation against a specification than it is in many imperative
languages due, in part, to the management of side effects in Haskell. This is
more difficult to do using an imperative language such as C, as they provide no
restrictions on where side effects can occur.

@@

Note the instance definition is automatically generated from the \ttt{Generic}
instance.
